### 2019-06-05 reports/thesis/chapters/2_dataCollection.tex

\cite{brierley2018optimized} did something similar by comparing a projection of the test sample, with no voids, with a simulation of that projection with voids added in the CAD. The experiment presented here is the other side of the coin, putting voids in the physical test sample rather than in the simulated projection. This makes the experiment more realistic by attempting to detect real voids. Being able to detect voids in projection space suggest quality control can be done in projection space, rather than reconstruction space, to speed up the quality control procedure.

@@

X-ray projections were obtained using the \emph{Nikon XT H LC 225/320} x-ray CT scanner (\emph{Nikon Metrology, UK}) together with a \emph{Perkin Elmer XRD 1621 (Perkin Elmer, US)} detector. The target material in the x-ray source is tungsten. The sensor in the detector is made up of 2 rows and 16 columns of panels. The sensor has dimensions of $\SI{409.6}{\milli\metre}\times\SI{409.6}{\milli\metre}$ with produced a projection of $\SI{2048}{\pixel}\times\SI{2048}{\pixel}$ in size \citep{perkinelmer2006xrd}. Therefore the scale of each pixel is $\SI{200.0}{\micro\metre\per\pixel}$. The projections were cropped to $\SI{2000}{\pixel}\times\SI{2000}{\pixel}$ to remove boundary effects. The gain and offset were adjusted by the engineers to produce a projection with good contrast, each pixel then has a grey value in units of analogue to digital units (\SI{}{\adu}).

Greyscale projections were taken in addition to the projection of the test object. These are projections with nothing to scan at different powers used in the x-ray tube. The power was varied by fixing the potential difference and varying the current. The greyscale projections were used for calibration such as shading correction.

Replicate projections of the test object and greyscale projections were obtained by repeating the scan. These replicated projections were used to study the noise observed in the projections.

@@

@@

3 datasets were collected and named \texttt{AbsNoFilter}, \texttt{AbsFilter} and \texttt{TiFilter}. Projections of the ABS test object were taken in \texttt{AbsNoFilter} and \texttt{AbsFilter}, the titanium test object was used in \texttt{TiFilter}. 2 angular projections were taken for all datasets as well as greyscale projections. To investigate the effects of beam hardening, no x-ray filter was used in \texttt{AbsNoFilter}, a filter was used in \texttt{AbsFilter}.

@@

Shading correction, also known as flat field correction, aims to eliminate any spatial variation in sensitivity of the projections such as panel and spot effects. Shading correction is typically done using the greyscale projections and how the pixels respond to different powers. For example the black and white images can be used to correct the projection using
\begin{equation}
U_{x,y} = \dfrac{N_{x,y}-\text{black}_{x,y}}{\text{white}_{x,y}-\text{black}_{x,y}}\times B+A
\end{equation}
where $N_{x,y}$ is the obtained projection, $U_{x,y}$ is the shading corrected projection and $A$ and $B$ are some user defined constants \citep{young2000shading, munzenmayer2003enhancing}. This can be extended to include more greyscale projections by using the fact that the grey value respond linearly to the power of the x-ray source \citep{seibert1998flat}. More generally, shading correction can be expressed as
\begin{equation}
U_{x,y} = N_{x,y} \beta_{x,y} + \alpha_{x,y}
\end{equation}
where $\alpha_{x,y}$ and $\beta_{x,y}$ are some spatially varying functions \citep{munzenmayer2003enhancing}. However there is an argument that this model has limitations because $\alpha_{x,y}$ and $\beta_{x,y}$ depends on the energy of each photon, thus beam hardening could cause inaccuracies in shading correction \citep{davidson2003limitations}.

@@

Let $N_{x,y}(P)$ be the grey value of pixel $(x,y)$ after being exposed to x-rays of power $P$ for some fixed exposure time. The power can be varied at the x-ray source when obtaining the greyscale projections or via attenuation assuming no beam hardening. Let $U_{x,y}(P)$ be the shading-free pixel at $(x,y)$. Assume that
\begin{equation}
U_{x,y}(P) = N_{x,y}(P)\beta_{x,y}+\alpha_{x,y}
\end{equation}
where $\beta_{x,y}$ and $\alpha_{x,y}$ is some constant which varies spatially. Suppose when

@@

\begin{figure}
  \centering
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_interpolation.eps}
      \caption{Example gain curves}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_gradient_bw.eps}
      \caption{Normalised gain map}
    \end{subfigure}
  }
  \caption{Normalised gain map from bw shading correction is shown in b). They were obtained by using the gradient in the example shown in a) for 3 random pixels.}
  \label{fig:data_shadingCorrectionExample_gainMap}
\end{figure}

>>>>

\cite{brierley2018optimized} did something similar by comparing a projection of the test sample, with no voids, with a simulation of that projection with voids added. The experiment presented here is the other side of the coin, putting voids in the physical test sample rather than in the simulated projection. This makes the experiment more realistic by attempting to detect real voids. Being able to detect voids suggest quality control can be done in projection space, rather than reconstruction space, to speed up the quality control procedure.

@@

X-ray projections were obtained using the \emph{Nikon XT H LC 225/320} x-ray CT scanner (\emph{Nikon Metrology, UK}) together with a \emph{Perkin Elmer XRD 1621 (Perkin Elmer, US)} detector. The target material in the x-ray source is tungsten. The sensor in the detector is made up of 2 rows and 16 columns of panels. The sensor has dimensions of $\SI{409.6}{\milli\metre}\times\SI{409.6}{\milli\metre}$ which produced a projection of $\SI{2048}{\pixel}\times\SI{2048}{\pixel}$ in size \citep{perkinelmer2006xrd}. Therefore the scale of each pixel is $\SI{200.0}{\micro\metre\per\pixel}$. The projections were cropped to $\SI{2000}{\pixel}\times\SI{2000}{\pixel}$ to remove boundary effects. The gain and offset were adjusted by the engineers to produce a projection with good contrast, each pixel then has a grey value in units of analogue to digital units (\SI{}{\adu}).

Greyscale projections were taken in addition to the projection of the test object. These are projections with nothing between the source and the detector with the x-ray tube at different powers. The power was varied by fixing the potential difference and varying the current. The greyscale projections were used for calibration such as shading correction. The greyscale projection with the x-ray turned off is called the black image. The greyscale projection with the x-ray set up the same when obtaining the test object projection is called the white image.

Replicate test object projections and greyscale projections were obtained by repeating the acquisition. These replicated projections were used to study the noise observed in the projections.

@@

\emph{aRTist} was used to simulate the test object projection and all greyscale projections except for the black image. The black image was simulated by producing an uniform image with grey value the mean over the obtained black image. The engineers used numerical methods to align the simulated projection with the obtained projection.

@@

3 datasets were collected and named \texttt{AbsNoFilter}, \texttt{AbsFilter} and \texttt{TiFilter}. Projections of the ABS test object were taken in \texttt{AbsNoFilter} and \texttt{AbsFilter}, the titanium test object was used in \texttt{TiFilter}. 2 angular projections were taken for all datasets. Greyscale projections were obtained as well. To investigate the effects of beam hardening, no x-ray filter was used in \texttt{AbsNoFilter}, a filter was used in \texttt{AbsFilter}.

@@

Shading correction, also known as flat field correction, aims to eliminate any spatial variation in sensitivity of the projections such as panel and spot effects. Shading correction is typically done using the greyscale projections and how the pixels respond to different powers. For example the black and white image, or images when averaging over replications, can be used to correct the projection using
\begin{equation}
U_{x,y} = \dfrac{N_{x,y}-\text{black}_{x,y}}{\text{white}_{x,y}-\text{black}_{x,y}}\times B+A
\label{eq:data_shadingCorrectionOld}
\end{equation}
where $N_{x,y}$ is the obtained projection, $U_{x,y}$ is the shading corrected projection and $A$ and $B$ are some user defined constants \citep{young2000shading, munzenmayer2003enhancing}. This can be extended to include more greyscale projections by using the fact that the grey value respond linearly to the power of the x-ray source \citep{seibert1998flat}. More generally, shading correction can be expressed as
\begin{equation}
U_{x,y} = \beta_{x,y} N_{x,y} + \alpha_{x,y}
\end{equation}
where $\alpha_{x,y}$ and $\beta_{x,y}$ are some spatially varying functions \citep{munzenmayer2003enhancing}. However there is an argument that this model has limitations because $\alpha_{x,y}$ and $\beta_{x,y}$ actually depend on the energy of each photon, thus beam hardening could cause inaccuracies in shading correction \citep{davidson2003limitations}.

@@

Let $S_{x,y}(P)$ be the greyscale projection when exposed to x-rays produced by an x-ray tube of power $P$ for some fixed time exposure $t$. $S_{x,y}(P)$ may be averaged over replications. Let $N_{x,y}$ be the obtained projection of the test sample when exposed to x-rays produced by an x-ray tube of power $P_\text{proj}$ for some fixed time exposure $t$. Therefore the black and white image can be expressed as $\text{black}_{x,y}=S_{x,y}(0)$ and $\text{white}_{x,y}=S_{x,y}(P_\text{proj})$ respectively.

The shading free image $U_{x,y}$ is not truly known, but it should expected that the shading corrected greyscale projection should be flat with some noise, in other words $\expectation\left[S_{x,y}(P)\right]=\mu_{S}(P)$ and $\variance\left[S_{x,y}(P)\right]=\sigma_{S}^2(P)$ for all $x=1,2,\cdots,L$ and $y=1,2,\cdots,H$. Suppose $\mu_{S}(P)$ was estimated using the within projection mean
\begin{equation}
\overline{S}(P) = \dfrac{1}{\text{WH}}
\sum_{x=1}^W\sum_{y=1}^H S_{x,y}(P) \ .
\end{equation}
Consider a pixel at $(x,y)$, shading correction was done by fitting a linear regression on
\begin{equation}
\overline{S}(P) = \beta_{x,y} S_{x,y}(P) + \alpha_{x,y} \quad(+\varepsilon)
\end{equation}
for $P\in \mathfrak{P}$ where $\mathfrak{P} = \left\{0,P_1,P_2,\cdots, P_\text{proj}\right\}$ are the powers used for the greyscale projections. $\varepsilon$ is a random variable and an error term, it is included only for formality purposes. Let $b_{x,y}$ and $a_{x,y}$ be the estimated parameters of $\beta_{x,y}$ and $\alpha_{x,y}$ from the linear regression respectively. Given a projection $N_{x,y}$, the shading corrected projection $U_{x,y}$ is
\begin{equation}
U_{x,y} = b_{x,y} N_{x,y} + a_{x,y}
\end{equation}
or in the form of Equation \eqref{eq:data_shadingCorrectionOld}
\begin{multline}
U_{x,y} = \dfrac{N_{x,y}-\text{black}_{x,y}}{\text{white}_{x,y}-\text{black}_{x,y}}\times \left[b_{x,y}(\text{white}_{x,y}-\text{black}_{x,y})\right]\\+\left[b_{x,y} \text{black}_{x,y} + a_{x,y}\right] \ .
\end{multline}
In full, the equations for $b_{x,y}$ and $a_{x,y}$ are given as
\begin{equation}
b_{x,y} = \dfrac{
  \sum_{P\in\mathfrak{P}}(S_{x,y}(P) - \overline{S}_{x,y})(\overline{S}(P) - \overline{S})
}{
  \sum_{P\in\mathfrak{P}}(S_{x,y}(P) - \overline{S}_{x,y})^2
}
\end{equation}
and
\begin{equation}
a_{x,y} = \overline{S} - b_{x,y}\overline{S}_{x,y}
\end{equation}
where $\overline{S}_{x,y}$ is the between projection mean
\begin{equation}
\overline{S}_{x,y} = \dfrac{1}{|\mathfrak{P}|}\sum_{P\in\mathfrak{P}}S_{x,y}(P)
\end{equation}
and $\overline{S}$ is the global mean
\begin{equation}
\overline{S} = \dfrac{1}{|\mathfrak{P}|}\sum_{P\in\mathfrak{P}}\overline{S}(P) \ .
\end{equation}
This type of shading correction shall be referred to as linear shading correction. Expressing shading correction in this way has the advantage that there are no user defined constants.

An example of the linear regression is shown in Figure \ref{fig:data_shadingCorrectionExample_gainMap} where 3 random pixels were chosen for illustration. By plotting the within projection mean versus the grey value for a particular pixel, a linear relationship can be observed. The gradient varied for different pixels which correspond to different sensitivities. The resulting shading correction for the \texttt{AbsNoFilter} projection is shown in Figure \ref{fig:data_shadingCorrectionExample_image}. It can be observed that the shading correction remove panel and spot effects from the background and test object.

\begin{figure}
  \centering
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_interpolation.eps}
      \caption{Linear regression}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_gradient_linear.eps}
      \caption{$b_{x,y}$}
    \end{subfigure}
  }
  \caption{For each pixel, a linear regression was fitted on the within projection mean versus the grey value for each greyscale projection. 3 random pixels were used to illustrate this in a). b) shows the fitted gradient for all pixels.}
  \label{fig:data_shadingCorrectionExample_gainMap}
\end{figure}

\begin{figure}
  \centering
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_image_null.eps}
      \caption{No shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_image_bw.eps}
      \caption{Linear shading correction}
    \end{subfigure}
  }
  \caption{Projection of \texttt{AbsNoFilter} with and without shading correction}
  \label{fig:data_shadingCorrectionExample_image}
\end{figure}

A variation of the shading correction which uses only the black and white image such that $\mathfrak{P}=\left\{0,P_\text{proj}\right\}$ shall be known as BW shading correction.

@@
